Insert the article title here

### 2020-07-23 tex/results.tex
add more context and explanations on rockstuhl

We decided to replicate one of the results that they present on Fig.14 of their paper, which 
presents the scattering cross section of a SiC rectangular cylinder for three different object 
sizes. To complain with our quasistatic approach ($\lambda > d$ where $d$) we chose the particular 
case where a=672 nm and b=328 nm.

@@

Based on the reuslts of the grid independence stud we decided to we used the density of the cube as a reference to produce the meshes for the replication 
of figures 14a and 14b on Rockstuhl's work (case a1=672, b=328). This simulation is a "rectangular cylinder" of 
dimensions (we chose a case that will go well with our quasistatic model) are $a=672$ nm and $b=328$ nm.

Effect of extended third dimension (in our case this is the y axis) are in Figures \ref{fig:ext_y_14} and

@@

\begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.45\textwidth]{ext_y_14a.pdf}}
    \subfloat{\includegraphics[width=0.45\textwidth]{ext_y_14b.pdf}} 
    %\caption{Extension of third dimension (y-axis) study for the case of rectangle prism of dimensions a=672 nm and b= 328 nm.
    %        Attempt of replication of Figure 14 a on Rockstuhl paper (case a1). In this case we have the constant 
    %        electric field parallel to the short dimension (b), and the geometry is in air. 
    %        Normalized (by max) Extinction cross section of a rectangle for two different y-values in the 
    %        short edge configuration (electric field parallel to the shorter dimension)}
    %\label{fig:ext_y_14a}
    %\label{fig:ext_y_14b}
    \caption{THIS IS A BIG CAPTION}
    \label{fig:ext_y_14}   
 \end{figure}

We see that as we elongate the third dimension the extra peaks start fading.

At this point we noticed that the mesher (trimesh) was not generating a uniform mesh. We created our 
own mesher, and tested the difference. Moreover, the paper mentioned that they rounded the corners of their
"rectangular cylinder". We were able to give our mesh as input to trimesh and round the edges but we were not able 
to know how the roundness was related to the arc of the curvature. This were parameters with no physical meaning, 
therefore we decided to go with the default setting.

\begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.45\textwidth]{tri_reg_round_14a.pdf}}
    \subfloat{\includegraphics[width=0.45\textwidth]{tri_reg_round_14b.pdf}}
    \caption{Normalized (by max) Extinction cross section of a rectangle. Original trimesh, regular, and regular with 
    roundness. Short edge configuration (electric field parallel to the shorter (left) dimension)}
    \label{fig:tri_reg_round_14}
 \end{figure}

 Finally with all this info, here is the replication of Figures 14a and 14b.

 \begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.45\textwidth]{replication_14a.pdf}}
    \subfloat{\includegraphics[width=0.45\textwidth]{replication_14b.pdf}}

    \caption{Normalized (by max) Extinction cross section of a rectangle. Replication of 
    the short (long) edge configuration (electric field parallel to the shorter (longer) dimension)}
    \label{fig:rep_14}
 \end{figure}

>>>>

We decided to replicate one of the results that they present on Fig.14 of their paper, which 
presents the scattering cross section of a SiC rectangular cylinder for three different object 
sizes. To comply with our quasistatic approach ($\lambda > d$ where $d$) we chose the particular 
case where a=672 nm and b=328 nm.

@@

We chose to replicate the result of Rocksuthl et al. presented in Figure 14. In particular the case where $a=672$ nm 
and $b=328$ nmn, since these dimension comply with the requirements of the quasistatic approximation.
They present the normalized scattering cross section of a SiC rectangular cylinder, and they perform simulation 
for two different setups. In Rockstuhl Figure 14 (left) they have the wave vector (illumination) along the long 
side of the geometry, which means that the electric field is parallel to the short side of the rectangle. Following, 
a similar analysis Rockstuhl Figure 14 (right) they have the wave vector (illumination) along the short
side of the geometry, which means that the electric field is parallel to the long side of the rectangle. These orientations,
correspond to the images (A) and (B) in the sketch presented in Figure \ref{fig:rectangle_sketch}.

Based on the results of the grid independence stud we decided to we used the density of the cube as a reference to 
produce the meshes for the replication of figures 14a and 14b on Rockstuhl's work (case a1=672, b=328). For the third 
dimension we needed to chose a value that represents "infinity". To achieve this, we perform a study on the effects of 
elongate the third dimension. In Figure \ref{fig:ext_y_14} we present the results for two different values of the 
third dimension, $y=1344$ nm (2xa) and $y=2688$ nm (4xa). 
We see that as we extend the third dimension the intensity of some peaks decreases, this is because some
of the peaks are related to the third dimension. Therefore, from now on we use $y=y=2688$ nm. It is worth 
noting that we could have increased this value more, however, the simulations will become computational
more expensive and we will still have the effects of having a 3D model.

@@

\begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.45\textwidth]{ext_y_14a.pdf}}
    \subfloat{\includegraphics[width=0.45\textwidth]{ext_y_14b.pdf}} 
    \caption{Effect of the elongation of the third direction ($y$) on the 
        extinction cross section of a rectangular prism of SiC of dimensions $a=672$ nm 
        and $b=328$ nm, submerged in air and under a constant electric field 
        parallel to the z-axis. The left plot corresponds to a configuration such that the electric 
        field is parallel to $b$ (configuration (A) on Figure \ref{fig:rectangle_sketch}), while the 
        right plot corresponds to a configuration such that the electric field is 
        parallel to $a$ (configuration (B) on Figure \ref{fig:rectangle_sketch}}
    \label{fig:ext_y_14}   
 \end{figure}

To generate the meshes for these simulations, we used the open source software Trimesh 
(\url{https://github.com/mikedh/trimesh}), but we realized that it was not producing a 
uniform mesh and that it was not possible to produce regular triangles with the functions 
available. To overcome this, we created our own mesh using python scripts, and therefore 
obtain uniform meshes. We wanted to study the effect of a uniform mesh as well as the effect
on rounding the edges. We wanted to round the edges since in Rockstuhl work this was mentioned 
as a factor that will introduce extra peaks on the response. We were not able to control the 
roundness as a function of arc of curvature or the dimensions of the rectangular prism, so we 
decided to use the default settings on Trimesh. Figure \ref{fig:tri_reg_round_14} shows the 
results on the effect of uniformity and roundness. You can see that the second peak is not
present in the green curve, which can be attributed to the effect of the roundness. This is 
consistent with the results on Rockstuhl's work.

\begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.45\textwidth]{tri_reg_round_14a.pdf}}
    \subfloat{\includegraphics[width=0.45\textwidth]{tri_reg_round_14b.pdf}}
    \caption{ Effect of uniformity and roundness on the mesh on the 
    extinction cross section of a rectangular prism of SiC of dimensions $a=672$ nm, 
    $b=328$ nm and $y=2688$ nm, submerged in air and under a constant electric field 
    parallel to the z-axis}
    \label{fig:tri_reg_round_14}
 \end{figure}

Once we have found the "best" possible geometry approximation, we show how our results 
(green curve in Figure \ref{fig:tri_reg_round_14}) compare 
with the original results from Rockstuhl's Figure 14. We have obtained Rockstuhl's curves by using 
the WebPlotDigitizer (\url{https://apps.automeris.io/wpd/}). The replication results are 
presented in Figure \ref{fig:rep_14}. We can say that the main peaks presented in Rockstuhl et al. are 
successfully replicated. While we still have the presence of a third peak in our results, we believe 
this is a consequence of the 3D nature of our geometry.

 \begin{figure}
    \centering
    \subfloat{\includegraphics[width=0.45\textwidth]{replication_14a.pdf}}
    \subfloat{\includegraphics[width=0.45\textwidth]{replication_14b.pdf}} 
    \caption{Replication of Figure 14 from Rockstuhl 2005. Extinction cross section of a
    rectangular prism of SiC of dimensions $a=672$ nm, $b=328$ nm and $y=2688$ nm, submerged
    in air and under a constant electric field parallel to the z-axis.}
    \label{fig:rep_14}
 \end{figure}
